---
title: "Comparison of preventive and disease related tweets in #Obesity"
author: "Shekhar Karmarkar"
date: "12/4/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F)
```

```{r}
# load necessay library
require(ggformula)
require(dplyr)
```


## Introduction:

Step one of project is done in python.  
Twitter is used to collect tweets related to #Obesity.  
The tweets text is collected in data frame.   
Duplicate tweets are deleted.  
It is confirmed that the tweet text contains word 'obesity'.  
Two lists of words are created -   
1. The words related to preventive aspect of obesity (aka pre_obesity)   
2. The words related to disease aspect of obesity (aka post_obesity)  

Each tweet is used to count the total words related to both lists.   
A tweet can contain words from both lists, and they are counted separately.  
Dataframe is created and stored as csv file.  

This is second step of project carried out in R.

## Load Data from csv

```{r}
# load data from csv
df <- read.csv('obesity.csv')
str(df)
```
# Counting total number of words in both lists

```{r}
pre = sum(df$pre_count)
post = sum(df$post_count)
total = pre + post
print(paste('Total number of tweets used  are ', nrow(df)))
print(paste('Total number of words from pre_obesity list are ', pre))
print(paste('Total number of words from post_obesity list are ', post))
print(paste('Total number of words from both lists are ', total))
```

## Proportion test 

The test is used to compare proportion of tweets from both lists.  
It is one sample proportion test.  

### Hypothesis: 
**Null Hypothesis:** The number of words from pre_obesity list and post_obesity list are same.    
$H_0$ : p = 0.5  
**Alternate Hypothesis:** The number of words from pre_obesity list and post_obesity list are not same.  
$H_a$ : p $\neq$ 0.5  

### Test :   
```{r}
# data:  pre out of total
# X-squared = 0.90163, df = 1, p-value = 0.3423
# alternative hypothesis: true p is not equal to 0.5
# 95 percent confidence interval:
#  0.4731279 0.5092223
# sample estimates:
#         p 
# 0.4911637 
prop.test(x = pre, n = total, p = 0.5, alternative = 'two.sided', conf.level = 0.95)
```

### Conclusion :  
As p-value is 0.34, we do not reject null hypothesis.  
With 95 % confidence, we can say that total number of words related preventive aspect of obesity and disease aspect of obesity are same in tweets.



-------------------------

This is summary of both list counts.  
It can be seen that summary is almost similar.  


```{r}
summary(df$pre_count)
summary(df$post_count)
```

The objects are created for graph creation.

```{r}
# pre_obesity list grouped by number of words per tweet

obj1 <- df %>% group_by(pre_count) %>% summarise(num = n())
```

```{r}
# post_obesity list grouped by number of words per tweet
obj2 <-  df %>% group_by(post_count) %>% summarise(num = n())
```





```{r}
# object created to graph total number of words 
tweets <- c(sum(df$pre_count), sum(df$post_count))
col <- c('Pre obesity','Post obesity')
obj3 <- data.frame(col,tweets)
obj3
```



```{r}
# distribution of words in tweets
color1 = c('purple','orange','cyan','black','lightblue','red','cyan','orange','pink','grey','red','blue')
gf_col(data = obj1, gformula = num ~ pre_count, fill = color1) %>% 
  gf_labs(x='Pre obesity word count', y = 'Number of tweets', title = 'Distribution of pre obesity words in tweets' , subtitle = 'From total 2163 tweets') 
    
```

```{r}
gf_col(data = obj2, gformula = num ~ post_count, fill = color1) %>% 
  gf_labs(x='Post-obesity word count', y = 'Number of tweets', title = 'Distribution of post- obesity words in tweets' , subtitle = 'From total 2163 tweets')
```

```{r}
gf_col(data = obj3, gformula = tweets ~ col, fill = c('cyan','purple')) %>% 
  gf_labs(x='Type of list', y = 'word count in all tweets', title = 'Number of words from both lists', subtitle = 'From total 2163 tweets')
 
  
```


